\chapter{Acknowledgement}
I want to first thank my thesis advisor Professor
Dipankar Maitra for giving me inspiring instructions and enormous supports when I was working on this thesis.  Professor Maitra encouraged me to present my work in different conferences, which push me make progresses along this process. Professor Maitra helped me go through many tough situations and gave me confidence when I was in troubles. Without his support, I could not accomplish this thesis and learn so many physics and astronomy knowledge.

Then, I want to thank my parents and other family members for being supportive during my four-year study at Wheaton. I had so many wonderful experiences at Wheaton and all of these cannot exist without my family's supports. I want to thank my mother who teaches me to become a dedicated person and my dad who is willing to know my thesis and give me encouragements when things did not go well. 

I want to thank all professors who
reviewed this thesis and provided useful feedbacks.
These professors are four members of my thesis committee: Professor Dipankar Maitra, Professor John Collins,
Professor Jason Goodman, and Professor Rachel Decoste.

I want to thank Dr. Herman Marshall from MIT Kavli Institute who gave me helpful advice when I was working on this thesis, and Prof. Michael Nowak from Washington University of St. Louis and Dr. David Huenemoerder from MIT Kavli Institute who answered my questions through email several times.

I want to thank all my friends who cheered me up when I was down during this tough year. I would like to especially thank my friend Zhuo Chen, who helped me in so many situations and added laughter to my life; Cheng Zhang, my role model, who keeps giving me inspirations in math study and adding fun to my life; Shi Shen, who always takes care of me and lets me know so many interesting things; and my sister and friend Xinru Liu, who always stands with me and exchanged knowledge with me when we are both working on theses.

I want to thank all professors in math and physics department who let me realize the beauty of math and physics. Before entering the college, I never thought that I could be majoring in either math or physics. With their helps, I was able to learn so many wonderful knowledge and discover the potentials of myself.

Finally I want to thank again all my dear friends
for these fun and memorable four years of college.
Most importantly, I want to express my gratitude to all professors who I had classes with. They not only taught me with knowledge, but also prepared me to face future challenges.